---
title: Environmental opporunities among secular and religious New Zealanders
author: "Joseph Bulbulia"
date: "Biola Jan 9 2021"
output:
  ioslides_presentation: default
  slidy_presentation: default
  extra_dependencies: ["rotating", "booktabs", "graphicx","longtable","amsmath","amsfonts","amssymb"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load_libraries, echo=FALSE, include=FALSE}
source("libs.R")
source("funs.R")
```

```{r  echo=FALSE, include=FALSE}
# setup

# read data
d <- data_read()

# take longitudinal cases (i.e more than one response)
dom <- data_take_longitudinal_cases( d )

# show unique id
length(unique(dom$Id)) 

# years
max(dom$years)


# label changes
dom$Your_Future_Security <- dom$SWB.SatPWI03
dom$MostNZPoliciesServeGrGood <- dom$SysJust04
dom$Religious <-
  factor(dom$Religious, labels = c("Not_Religious", "Religious"))

table1::label(dom$Env.ClimateChgReal) <- "Climate Change Reality"
table1::label(dom$Env.ClimateChgCause) <-
  "Humans Cause Climate Change"
table1::label(dom$EnvEfficacy) <- "Human Efficacy"
table1::label(dom$Env.SacMade) <- "Sacrificed for Environment"
table1::label(dom$Env.SacWilling) <-
  "Willing to Sacrifice Environment"
table1::label(dom$Env.MotorwaySpend) <- "Gov Motorway Spend"
table1::label(dom$Env.PubTransSubs) <-
  "Gov Subsidy Public Transport"
table1::label(dom$Env.NATIVE.SPECIES) <- "Protect NZ Species"
table1::label(dom$Env.SatNZEnvironment) <-
  "Sat Quality NZ Environment"
table1::label(dom$Env.ClimateChgConcern) <-
  "Deeply Concerned About Climate"
dom$Your_Future_SecurityS = scale(dom$Your_Future_Security)
dom$K6S = scale(dom$KESSLER6)

dom$Env.SatNZEnvironmentS <- scale(dom$Env.SatNZEnvironment)
dom$Your_Future_SecurityS <- scale(dom$Your_Future_Security)
dom$Env.ClimateChgConcernS <- scale(dom$Env.ClimateChgConcern)
dom$EnvEfficacyS <- scale(dom$EnvEfficacy)
dom$RelidS <- scale(dom$Relid)
```



## Background: New Zealand Attitudes and Values Study
## What is the New Zealand Attitudes and Values Study (NZAVS)?
    - Planned 20-year longitudinal study, currently in its 11th year.
    - Postal questionnaire.
    - Sample frame drawn randomly from NZ Electoral Roll.
    - Large multidisciplinary research team.
    - Focus on personality, social attitudes, values, religion, adult character development, identity, employment, experiences of discrimination, well-being and health, and {\bf environmental attitudes}.
    - Current sample contains > 42,000 unique people, or 1.45\% of the adult NZ population (we have responses from 61,535 individuals.

##

```{r}
 table1::table1(
  ~ Env.ClimateChgReal + Env.ClimateChgCause + EnvEfficacy + Env.SacMade + Env.SacWilling + Env.SatNZEnvironment + Env.ClimateChgConcern |
    Wave,
  data = dom,
  overall = T,
  transpose = T
)
```


##
```{r , includ=FALSE}
mll <-
  lmer(Env.SacMade ~ years * (Env.ClimateChgConcernS * RelidS) + (1 |
                                                                    Id),
       data = dom)
```

```{r, echo = FALSE}
plot(ggpredict(mll, terms = c(
  "years", "Env.ClimateChgConcernS", "RelidS"
)))
```

       
       


<div class="notes">
This is my *note*.

- It can contain markdown
- like this list
</div>


## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

